Real-time resolving assembly graph by ONT long reads data

### 2019-11-15 paper.tex
add zymo
adding zymo result

%Set abstract (see below)
\abstract{
A real-time assembly pipeline for Oxford Nanopore Technology (ONT) data is important for either saving sequencing resources or reducing turnaround time for data analyses. The previous approach from \npscarf{} provided a greedy fast-response, auto-correct streaming algorithm for such task but was relatively prone to mis-assemblies compared to other graph-based methods. 
Here we present \npgraph{}, a real-time hybrid assembly software using the assembly graph instead of the separated pre-assembly contigs. It is able to produce more complete genome assembly by resolving the path finding problem on the assembly graph using long reads as the traversing guide. 
The applications on synthetic and real data set of isolate genomes show improved accuracy while still maintain the required computational cost at very low level. In addition, the GUI feature can provide users a comprehensive look-and-feel of the whole assembly process. The tool and source code is available at \url{https://github.com/hsnguyen/assembly}.
}

@@

\subsection*{Metagenomics assembly}
We further used \npgraph{} on three mock communities to study the performance of this approach in metagenomics co-assembly application.

>>>>

%Set abstract (see below)
\abstract{
A real-time assembly pipeline for Oxford Nanopore Technology (ONT) data is important for either saving sequencing resources or reducing turnaround time for data analyses. The previous approach from \npscarf{} provided a greedy fast-response, auto-correct streaming algorithm for such task but was relatively prone to mis-assemblies compared to other graph-based methods. 
Here we present \npgraph{}, a real-time hybrid assembly software using the assembly graph instead of the separated pre-assembly contigs. It is able to produce more complete genome assembly by resolving the path finding problem on the assembly graph using long reads as the traversing guide. 
The applications on synthetic and real data set of isolate genomes show improved accuracy while still maintain the required computational cost at very low level. In addition, the GUI feature can provide users a comprehensive look-and-feel of the whole assembly process. The tool and source code is available at \url{https://github.com/hsnguyen/assembly}.
%=======
%A real-time assembly pipeline for Oxford Nanopore Technology (ONT) data is important for either better control of sequencing resources or quick turnaround of analyses. The previous approach from \npscarf{} provided a greedy fast-response, auto-correct streaming algorithm for such task but was relatively prone to mis-assemblies. Here we present another real-time hybrid assembler, \npgraph{}, that can work on the assembly graph instead of the pre-assembled contigs. The results show improved accuracy while still minimize the required computational cost. The tool is available at \url{https://github.com/hsnguyen/assembly}.
%>>>>>>> 2d4c481dd93902dfb2dabe46534a62e8a8c2058c
}

@@

\subsection*{Metagenomics assembly}
We further employed \npgraph{} on mock community data to study the performance of our method in metagenomics co-assembly problem.
In this application, sequencing data (including both short and long reads) from mixtures of ten microbial species of ZymoBIOMICS Microbial Community Standards \cite{Nick2019zymo} were used as input for \npgraph{}. 
The total genome size was estimated as 61.96 Mbp.
There were two settings for the input depending on the distribution of cell abundances in the mixture itself, namely even and log population.
On the other hand, 8 out of 10 genomes being sequenced were reconstructed by using PacBio sequencing (RSII and Sequel) previously \cite{Mcintyre2019zymo}, including \emph{Bacillus~subtills}, \emph{Enterococcus~faecalis}, \emph{Escherichia~coli}, \emph{Listeria~monocytogenes}, \emph{Pseudomonas~aeruginosa}, \emph{Saccharomyces~cerevisiae}, \emph{Salmonella~enterica} and \emph{Staphylococcus~aureus}. We evaluated the coassembly results by running $\mathtt{metaQUAST}$ given 8 PacBio assembly as references.

\begin{table}[!hpt]
\begin{center}
\caption{NGA50 improvement from $\mathtt{metaSPAdes}$ to \npgraph{} assembly on two mock communities ZymoLog and ZymoEven. The statistics were generated by $\mathtt{metaQUAST}$ v3.2 with 8 (out of 10) available PacBio references of individual isolates \cite{Nick2019zymo}.}
\label{table:zymo}
\begin{tabular}{|l|r|r|r|r|}
\hline
\multirow{2}{*}{\textbf{Community}} & \multicolumn{2}{|c|}{\textbf{ZymoEven}} & \multicolumn{2}{|c|}{\textbf{ZymoLog}} \\ \cline{2-5}
& $\mathtt{metaSPAdes}$ & \npgraph{} & $\mathtt{metaSPAdes}$ & \npgraph{} \\ \hline
\emph{B.~subtilis} & $23,386$ & $382,368$ & $35,390$ & $433,078$ \\ \hline
\emph{E.~coli} & $34,776$ & $1,108,989$ & $-$ & $-$ \\ \hline
\emph{E.~faecalis} & $23,340$ & $217,908$ & $-$ & $-$ \\ \hline
\emph{L.~monocytogenes} & $26,480$ & $520,012$ & $23,146$ & $130,284$ \\ \hline
\emph{P.~aeruginosa} & $59,372$ & $1,753,658$ & $161,816$ & $444,495$ \\ \hline
\emph{S.~aureus} & $26,058$ & $175,908$ & $-$ &$-$ \\ \hline
\emph{S.~cerevisiae} & $-$ & $-$ & $-$ & $-$ \\ \hline
\emph{S.~enterica} & $33,363$ & $4,242,458$ & $-$ & $-$ \\ \hline
\end{tabular}
\end{center}
\end{table}

To run \npgraph{} on the metagenomics data set, we firstly augmented binning information from using $\mathtt{metaBAT}$ \cite{Kang2015metabat} on the Illumina raw reads, before applying our method to the assembly graph generated by $\mathtt{metaSPAdes}$. The default parameter setting was remained as it was for isolate assembly.

In terms of Illumina data, Even community had been sequenced by MiSeq platform which generated about 43-fold coverage while the Log community`s short-read data had been obtained from an Illumina HiSeq 1500, for about 156X coverage.
Even though the total amount of base coverage from the latter was almost four-times richer than the former, its $\mathtt{metaSPAdes}$ assembly quality was lesser. This due to the fact of under-presented microbial cells from rare species in the log population that require much more input to compensate, resulting in significant smaller size of assembly contigs and more fragmented assembly graph (Supplementary Figure~\ref{supp_fig:npgraph_zymo}).

Table~\ref{table:zymo} shows the assembly improvement in terms of NGA50 after running \npgraph{} on the $\mathtt{metaSPAdes}$ initial graph.  
As expected from better quality assembly graph, the results for the Even community indicated significant more complete genomes recovered. 
There were 7 isolate genomes had been identified for this community, compared to only 3 from the more complicated log population.
\npgraph{} had been able to resolve the assembly graph efficiently for Even community, with the maximum NGA50 improvement for \emph{S.~enterica} from $33$ Kbp to $4.2$ Mbp. 
On the other hand, genomes from the Log community witnessed increasing length of aligned contigs as well, but not as huge as the other. The longest NGA50 contigs belongs to \emph{P.aeruginosa} of 445 Kbp, however, the counterpart from the Even community was 4-fold than that, at 1.75 Mbp.
The only exception was \emph{B.~subtilis}, where \npgraph{} can only resolved 382 Kbp correct length from the zymo even while the respective figure was 433 Kbp for the zymo log. It is noteworthy that for this case, initially the $\mathtt{metaSPAdes}$ assembly for the former was slightly better compared to the latter.
